### 2016-10-14 final_checks/DVCS-CAN-Meeting-Comments.tex
Update on the "final" answers

I also discussed with Raphael the necessity to explain in the section on 
Systematic uncertainties how the corresponding numbers in the numerical tables 
are generated. So far, the discussion is exclusively on the fitted ALU(90°), 
while the numbers in the Tables are bin-dependent.

@@

\begin{enumerate}
   \item \textcolor{blue}{Regarding the stability of the coherent $A_{LU}$ with 
      respect to the missing energy cut. I first remind you about the previous 
   study from the first round comments and the results we got. Then, I will 
present the new results after the CAN review committee suggestions. }

@@

 \item Following the CAN committee suggestions, we applied the requested cuts 
    to remove the tails and we extracted R for the different bins in the 
    missing energy. The results are presented in figure 
    \ref{fig:coherent_ME_bins_2}. Within the given error bars, the two sets of 
    results are compatible.

    \begin{figure}[tbp]
   \includegraphics[height=6.0cm]{fig/new_ME_Coh_bins.png}
   \includegraphics[height=6.0cm]{fig/e4Hegamma_e4Hepi0_Phi_ME.png}
   \hspace{-3.0cm} \includegraphics[height=6.5cm]{fig/new_BSA_coherent_ME.png}
   \hspace{-1.0cm} \includegraphics[height=6.5cm]{fig/new_coh_ME_alpha.png}
   \caption{from top to bottom and from left to right, coherent missing energy 
      binning, the corresponding background acceptance ratio from simulation, 
      the reconstructed beam-spin asymmetries as a function of $\phi$ (middle), 
   and the extracted asymmetry at $\phi = 90 ^{\circ}$ from fitting the 
asymmetries as a function of the mean missing energy in each bin.  }
   \label{fig:coherent_ME_bins_2}
    \end{figure}
\end{enumerate}

\item \textcolor{blue}{Regarding the listed bin by bin systematic errors, they 
   were extracted from the variation of the reconstructed asymmetries such as 
in figures 4.23 and 4.29 in the analysis note. The text is modified to include 
the extraction details, see the end of section 4.7.}

>>>>

I also discussed with Raphael the necessity to explain in the section on 
Systematic uncertainties how the corresponding numbers in the numerical tables 
are generated. So far, the discussion is exclusively on the fitted ALU(90$^\circ$), 
while the numbers in the Tables are bin-dependent.

@@

\begin{enumerate}
   \item \textcolor{blue}{Regarding the stability of the coherent $A_{LU}$ with 
      respect to the missing energy cut. We first remind the previous 
      exchange from the first round comments and the results we got. Then, we 
      present the new study after the CAN review committee suggestion.}

@@

 \item Following the CAN committee suggestion, we performed this study again
    recalculating the $\pi^0$ contamination for the different bins in the 
    missing energy. The results are presented in figure 
    \ref{fig:coherent_ME_bins_2}. The high missing energy bin is the
    most affected and goes up, closer to the value from the central point.    
    This is easily understood as this bin has a significantly higher $\pi^0$
    contribution. In conclusion, the central bin remains with a stronger 
    signal, however we want to point out that (i) this feature is not significant 
    due to the large error bars in regard to the size of the effect and 
    (ii) the variations are smaller than the 8\% systematic error we evaluated 
    from the rather arbitrary choice of exclusivity cuts. In conclusion, we
    believe that the cut is good as it is. The main reason being that 
    statistical errors already dominate the error budget, so we think it
    would be counter productive to reduce even more our data sample in hope to
    reduce the systematic error.

\newpage
    \begin{figure}[tbp]
   \includegraphics[height=6.0cm]{fig/new_ME_Coh_bins.png}
   \includegraphics[height=6.0cm]{fig/e4Hegamma_e4Hepi0_Phi_ME.png}
   \hspace{-3.0cm} \includegraphics[height=6.5cm]{fig/new_BSA_coherent_ME.png}
   \hspace{-1.0cm} \includegraphics[height=6.5cm]{fig/new_coh_ME_alpha.png}
   \caption{from top to bottom and from left to right, coherent missing energy 
      binning, the corresponding background acceptance ratio from simulation, 
      the reconstructed beam-spin asymmetries as a function of $\phi$ (middle), 
   and the extracted asymmetry at $\phi = 90 ^{\circ}$ from fitting the 
asymmetries as a function of the mean missing energy in each bin.  }
   \label{fig:coherent_ME_bins_2}
    \end{figure}
\end{enumerate}

\item \textcolor{blue}{Regarding the listed bin by bin systematic errors, they 
   were extracted from the variation of the reconstructed asymmetries such as 
in figures 4.23 and 4.29 in the analysis note. The end of section 4.7 has been 
modified to include the following details on our error bar calculation:}

In addition to evaluating the systematic uncertainties on $A_{LU}$ at $\phi = 
90^{\circ}$, we performed bin by bin, in $\phi$, extraction of these 
uncertainties. For instance, regarding the bin extraction from the source 'data 
binning' listed in table \ref{Table:systematic_uncertainties}, the uncertainty 
is calculated as the difference between the two reconstructed asymmetries.  
Similar procedures have been carried out for the other studies, and finally all 
the contributions were added quadratically. These systematic uncertainties will 
be shown with the final asymmetry results in the following chapter.
